Errata

### 2025-04-04 tex/Methodology.tex
Update dissertation files with new packages and refine section headings
Refine methodology and results discussion sections for clarity and accuracy
- Updated the methodology section to enhance the description of microbial community data analysis techniques, ensuring consistency in terminology and clarity in the explanation of statistical methods.
- Revised the results discussion to improve the flow of information regarding biocrusts' impact on soil aggregate stability, emphasizing their role in arid ecosystems and correcting citation formatting.
- Adjusted references to ensure proper citation

\subsection{Molecular Analyses}

@@

Microbial community data were analyzed using various multivariate techniques. Non-metric multidimensional scaling (NMDS) was used to visualize community structure and beta diversity \citep{Oksanen2013}. Permutational multivariate analysis of variance (PERMANOVA) assessed the significance of differences between groups (e.g., sites, horizons, time points), often followed by pairwise PERMANOVA for detailed comparisons \citep{MartinezArbizu2020} (Manuscripts 3 and 4). Distance-based redundancy analysis (dbRDA) identified environmental factors influencing community composition (Manuscript 4). Indicator species analysis revealed taxa associated with specific sites or horizons using the $indval$ function \citep{Dufrêne1997,Roberts2016} (Manuscript 4).

>>>>

\subsection{Molecular analyses}

@@

Microbial community data were analyzed using various multivariate techniques. Non-metric multidimensional scaling (NMDS) was used to visualize community structure and beta diversity \citep{Oksanen2013}. Permutational multivariate analysis of variance (PERMANOVA) assessed the significance of differences between groups (e.g., sites, horizons, time points), often followed by pairwise PERMANOVA for detailed comparisons \citep{MartinezArbizu2020} (Manuscripts 3 and 4). Distance-based redundancy analysis (dbRDA) identified environmental factors influencing community composition (Manuscript 4). Indicator species analysis revealed taxa associated with specific sites or horizons using the $indval$ function \citep{Dufrene1997,Roberts2016} (Manuscript 4).

### 2025-04-04 tex/Results_Discussion.tex
Update dissertation files with new packages and refine section headings
Refine methodology and results discussion sections for clarity and accuracy
- Updated the methodology section to enhance the description of microbial community data analysis techniques, ensuring consistency in terminology and clarity in the explanation of statistical methods.
- Revised the results discussion to improve the flow of information regarding biocrusts' impact on soil aggregate stability, emphasizing their role in arid ecosystems and correcting citation formatting.
- Adjusted references to ensure proper citation

These findings highlight that biocrusts contribute to soil structure by binding particles and microaggregates, likely through mechanisms involving fungal hyphae, cyanobacterial filaments, and the production of extracellular polymeric substances \citep{Six2004,Totsche2018}. While biocrusts influenced bulk C and N contents, the lack of a direct correlation between these bulk changes and stability across all sites suggests that the specific composition and micro-spatial arrangement of organic binding agents within aggregates, rather than just total C or N, are critical for stability \citep{Wagner2007}. The results emphasize the crucial role of biocrusts as primary stabilizing agents in arid and semi-arid ecosystems \citep{BelnapBüdel2016}, with their influence gradually yielding to vascular plants and associated soil organic matter dynamics in more humid environments.

@@

Soil properties varied across the climate gradient, reflecting differing weathering intensities and soil development stages relevant to hydrological and erosion responses. Notably, the inland semi-arid site (QdT) exhibited high biocrust cover despite lower water availability compared to the coastal SG site, likely due to protection from disturbance within a fenced area since 2011, fostering biocrust development \citep{Büdel2016}. Soil texture across sites was predominantly sandy loam, with clay content increasing southward, influencing water retention and infiltration pathways.

\subsection{Biocrust Influence on Water Flow and Sediment Transport}
\label{sec:BiocrustOnWaterSesimentsFlows}

>>>>

These findings highlight that biocrusts contribute to soil structure by binding particles and microaggregates, likely through mechanisms involving fungal hyphae, cyanobacterial filaments, and the production of extracellular polymeric substances \citep{Six2004,Totsche2018}. While biocrusts influenced bulk C and N contents, the lack of a direct correlation between these bulk changes and stability across all sites suggests that the specific composition and micro-spatial arrangement of organic binding agents within aggregates, rather than just total C or N, are critical for stability \citep{Wagner2007}. The results emphasize the crucial role of biocrusts as primary stabilizing agents in arid and semi-arid ecosystems \citep{BelnapBudel2016}, with their influence gradually yielding to vascular plants and associated soil organic matter dynamics in more humid environments.

@@

Soil properties varied across the climate gradient, reflecting differing weathering intensities and soil development stages relevant to hydrological and erosion responses. Notably, the inland semi-arid site (QdT) exhibited high biocrust cover despite lower water availability compared to the coastal SG site, likely due to protection from disturbance within a fenced area since 2011, fostering biocrust development \citep{Budel2016}. Soil texture across sites was predominantly sandy loam, with clay content increasing southward, influencing water retention and infiltration pathways.

\subsection{Biocrust influence on water flow and sediment transport}
\label{sec:BiocrustOnWaterSesimentsFlows}
